Data Builder

### 2019-04-04 notebooks/data_builder.Rmd
minimized type names, added support for L1 (see Main.java for flag)

```{r}
# read in new one
# DONT FORGET TO GET RID OF }"" lol
psp_L0 <- read_csv("../data/partial_L0_subtype.csv")

@@

# go to terminal, gzip it for Java
# DONT FORGET TO GET RID OF }"" lol
```

>>>>

```{r}
# read in new one
psp_L0 <- read_csv("../data/partial_L0_subtype.csv")

@@

# go to terminal, gzip it for Java
```
